SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-08-15 scipy-1.0/ckdtree.tex
Highlight things that need fixing

\textbf{Add a Figure to show the scaling, before and after.}
\textbf{perhaps give an example or some formula.}
(cite / mention faster implementions of paircounting algorithms / treecorr, corrfunc)

>>>>

\fixme{Add a Figure to show the scaling, before and after.}
\fixme{perhaps give an example or some formula.}
(cite / mention faster implementions of paircounting algorithms / treecorr, corrfunc)

### 2018-08-15 scipy-1.0/paper.tex
Highlight things that need fixing

% New Commands
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\code}[1]{\texttt{#1}}

@@

\textit{The Introduction section expands on the background of the work (some overlap with the Abstract is acceptable). The introduction should not include subheadings.}

@@

TODO

@@

\textit{The Discussion should be succinct and must not contain subheadings.}

@@

\textit{This section should include key issues: sparse arrays, ndimage pixel vs
point, splines, fftpack vs. np.fft and linalg vs. np.linalg, under-maintained
submodules.}

@@

\noindent Use the cite command for an inline citation, e.g. \cite{behnel2011cython}.

\section*{Acknowledgements (not compulsory)}

Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments. Grant or contribution numbers may be acknowledged.

@@

Must include all authors, identified by initials, for example:
A.A. conceived the experiment(s),  A.A. and B.A. conducted the experiment(s), C.A. and D.A. analysed the results.  All authors reviewed the manuscript.

@@

To include, in this order: \textbf{Accession codes} (where applicable); \textbf{Competing financial interests} (mandatory statement).

The corresponding author is responsible for submitting a \href{http://www.nature.com/srep/policies/index.html#competing}{competing financial interests statement} on behalf of all authors of the paper. This statement must be included in the submitted article file.

>>>>

% New Commands
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\fixme}[1]{\textcolor{red}{{#1}}}

@@

\fixme{The Introduction section expands on the background of the work (some overlap with the Abstract is acceptable). The introduction should not include subheadings.}

@@

\fixme{TODO}

@@

\fixme{The Discussion should be succinct and must not contain subheadings.}

@@

\fixme{This section should include key issues: sparse arrays, ndimage pixel vs
point, splines, fftpack vs. np.fft and linalg vs. np.linalg, under-maintained
submodules.}

@@

\section*{Acknowledgements}

\fixme{TODO}

%Acknowledgements should be brief, and should not include thanks to anonymous
%referees and editors, or effusive comments. Grant or contribution numbers may
%be acknowledged.

@@

\fixme{TODO}

%Must include all authors, identified by initials, for example: A.A.
%conceived the experiment(s),  A.A. and B.A. conducted the experiment(s), C.A.
%and D.A. analysed the results.  All authors reviewed the manuscript.

@@

\fixme{TODO}

%To include, in this order: \textbf{Accession codes} (where applicable);
%\textbf{Competing financial interests} (mandatory statement).

%The corresponding author is responsible for submitting a
%\href{http://www.nature.com/srep/policies/index.html#competing}{competing
%financial interests statement} on behalf of all authors of the paper. This
%statement must be included in the submitted article file.
